% 11/23/2015
\documentclass[draft,linenumbers]{afmjournal}
% \draftfalse
\usepackage{makecell} \usepackage{multirow} %AM for tables
\usepackage{booktabs} \drafttrue

\journalname{Agricultural and Forest Meteorology: When does VPD drive
  or reduce ET?}

\newcommand{\appropto}{\mathrel{\vcenter{
      \offinterlineskip\halign{\hfil$##$\cr
        \propto\cr\noalign{\kern2pt}\sim\cr\noalign{\kern-2pt}}}}}

\begin{document}

\title{When does vapor pressure deficit drive or reduce
  evapotranspiration?}


\authors{Adam Massmann\affil{a}, Pierre Gentine\affil{a}, Changjie
  Lin\affil{a,b}}

\affiliation{a}{Department of Earth and Environmental Engineering,
  Columbia University, New York, NY 10027} \affiliation{b}{State Key
  Laboratory of Hydroscience and Engineering, Department of Hydraulic
  Engineering, Tsinghua University, Beijing, CN 100084}

\correspondingauthor{Adam Massmann}{206-919-1364;
  akm2203@columbia.edu}

\begin{abstract}
  Increasing vapor pressure deficit increases atmospheric demand for  water, and vapor pressure deficit is expected to rise with  increasing greenhouse gases. While increased evapotranspiration (ET) in  response to increased atmospheric demand seems intuitive, plants are  capable of reducing ET in response to increased VPD by closing their  stomata, in an effort to conserve water. Here we examine which  effect dominates response to increasing VPD: atmospheric demand and  increases in ET, or plant physiological response (stomata closure)  and decreases in ET. We use Penman-Monteith, combined with  semi-empirical optimal stomatal regulation theory and underlying  water use efficiency, to develop a theoretical framework for  understanding how ET responds to increases in VPD.

  The theory suggests that for most environmental conditions and plant  types, plant physiological response dominates and ET decreases with  increasing VPD. Plants that are evolved or bred to prioritize  primary production over water conservation (e.g. crops) exhibit a  higher likelihood of atmospheric demand-driven response (ET  increasing). However for forest, grass, savannah, and shrub plant  types, ET more frequently decreases than increases with rising  VPD. This work serves as an example of the utility of  our simplified framework for disentangling land-atmosphere feedbacks  at multiple scales, including the characterization of ET response in  an atmospherically drier, enriched CO$_2$ world. 
\end{abstract}

\begin{keypoints}
\item ecohydrology, evapotranspiration, aridity, vapor pressure
  deficit, plant physiology, stomatal response
\end{keypoints}

\input{body.tex}


